---
title: "Chapter 2 Results"
author: "Yaya"
date: "10 August 2021"
output: 
  html_document: 
    toc: true
    toc_depth: 4
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
---

# Introduction

TL;DR:
These are results from the second chapter in my PhD using graphs and code copied from R scripts on 10 August 2021. 
Sections with asterisks** mark the sections with statistics to be used for the paper.

--------------

Here are the items included in this report:

_Necromass_

* quantity
  + prey products (both carcasses + fed to predators)
    - measured wet mass from all, calculated dry mass from calibration locusts
  + predator products 
    - directly measured dry mass prior to adding to soil microcosms

* quality 
  + prey products
    - analyzed from calibration locusts
  + predator products 
    - analyzed from feeding assay products


_Necrobiome_

Function in this experiment refers to rates of C the C mineralization.

1) Overall effect of predators on function: G, MA, WA
    + Phase 1
    + Phase 2
      - all treatments with animal products had lower function aka negative legacy
    + Cumulative overall

2) Computer predator products vs all predator products
    + Phase 1
      - calculate difference from litter-only control tubes
    + Phase 2
    + Cumulative overall

3) Predator products by feeding strategy 2x2
    + unscaled analysis
    + scaled to biomass
      - remove mantid prey remains treatment (too high)
      - spider wastes generated highest rates of mineralization, per gram
    
* Overall microcosm mineralization conclusions
  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# This is a new script for summarizing and visualizing the 
# IRGA data for poopy predators

#===== Setup: Libaries, import data ======
library(tidyverse)
library(ggpubr)
library(janitor)
library(viridis)
library(plotly)
library(gridExtra)
library(lme4)
library(dunn.test) ## for dunn.test
library(FSA) ## for dunnTest
library(readxl)
library(ARTool)
library(emmeans)

set.seed(20210926)

# remotes::install_github("coolbutuseless/ggpattern")
source(here::here('src/yaya_fxns.R'))
source("C:/Users/yaya/Dropbox/1 Ecologist/2 EXPERIMENTS/yaya_r_themes.R")

#create my own theme for these plots
theme_pp <- theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1),
                  panel.background = element_rect(fill = "#f9f9f9",
                                                  colour = "#f9f9f9"),
                  panel.border = element_rect(color = "black", fill = NA))

theme_dyn <- theme(axis.text.x = element_text(vjust = 1, hjust=0.5),
                   panel.background = element_rect(fill = "#f9f9f9",
                                                   colour = "#f9f9f9"),
                   panel.border = element_rect(color = "black", fill = NA))

bar_x_labels <- c('Grasshopper carcass',
                  'Mantid, All products', 
                  'Mantid, Prey remains', 
                  # 'Mantid, Excreta + egesta',
                  'Mantid, Wastes', 
                  'Spider, All products', 
                  'Spider, Prey remains', 
                  # 'Spider, Excreta + egesta', 
                  'Spider, Wastes', 
                  'Control, litter only')

bar_x_labels_short <- c('Grasshopper', 
                        'All', 'Remains', 'Wastes', #'Excreta, egesta',
                        'All', 'Remains', 'Wastes') #Excreta, egesta', 
# 'Litter only')

vir_8 <- viridis(8)
vir_4 <- viridis(4)



```

#. 

# Necromass properties

Import all IRGA data, amd summarize control data.

TO DO: some day, check the unique table of `r c('trt', 'ghop_fate', 'pred_prod')` and figure out why there is a set of rows with NA. 

```{r, message=FALSE, warning=FALSE}
## import big table with all relevant data
## this is all of the IRGA data, with columns for "origin dry mass" [locust mass] and "treatment added mass" [predator products] for each tube
imported_data <- readRDS(here::here("results/3_data_to_graph.rds")) %>% 
  ungroup() %>% 
  clean_names() %>%
  filter(trt != 'R',
         # trt != 'C',
         trt != 'WS', ## this it the treatment of only capture silk
         trt != 'WR',
         trt != 'WN') %>% ## this is for nest silk, and isn't relevant for this analysis 
  select(tube_id, trt, rep, ghop_fate, phase, phase_count, exp_count, 
         infer_tube_total_daily, origin_dry, trt_added_mass) %>% 
  mutate(pred_prod = substr(trt, 2, 2)) %>% 
  group_by(trt, rep) %>% 
  arrange(exp_count)


# add/fix grouping variables to partially cluster bar charts
## group_compute = 1 includes treatments that are ALL predator foraging by-products
## group_compute = 2 is everything else
imported_data$trt <- fct_relevel(imported_data$trt, 'G', 'MA', 'MR', 'ME', 'WA', 'WW', 'WE', 'WR', 'WS', 'WN')

imported_data$group_compute <- as.numeric(nrow(imported_data))
imported_data[which(imported_data$pred_prod == '' | imported_data$pred_prod == 'A'),]$group_compute <- 1
imported_data[which(imported_data$group_compute != 1),]$group_compute <- 2
imported_data[which(imported_data$trt == 'C'),]$ghop_fate <- 'control'
imported_data$ghop_fate <- fct_relevel(imported_data$ghop_fate, 'carcass', 'mantid', 'spider', 'control')

imported_data[which(imported_data$pred_prod == 'W' | imported_data$pred_prod == 'R'),]$pred_prod <- 'remains'
imported_data[which(imported_data$pred_prod == 'A'),]$pred_prod <- 'all'
imported_data[which(imported_data$pred_prod == 'E'),]$pred_prod <- 'excreta'
imported_data[which(imported_data$pred_prod == ''),]$pred_prod <- 'none'
imported_data$pred_prod <- fct_relevel(as_factor(imported_data$pred_prod), 
                                       'none', 'all', 'remains', 'excreta')

########## Setup: Control data subset ########
## This section of code is to subset the control tubes data and get the  
# treatment average for each day.  This table will be added to the rest of the 
# IRGA data

# extract the control data, and summarize
ctrl_data <- imported_data %>% 
  filter(trt == 'C') %>% 
  select(exp_count, trt, rep, infer_tube_total_daily) %>% 
  group_by(exp_count) %>%
  arrange(exp_count) %>% 
  summarize(trt = first(trt),
            ctrl_daily_mean = mean(infer_tube_total_daily),
            ctrl_daily_se = se(infer_tube_total_daily)) %>% 
  mutate(ctrl_cumul = cumsum(ctrl_daily_mean))
```


## A) Quantity: prey inputs to predators

This is the summary table of the system inputs and again in graphical form. These analyses are basically to show that there is no difference between the groups of prey bodies between treatments.  
(note, units are in mg)

```{r}
#### BEGIN DATA VISUALIZATION #####

#---- Figure: Plots comparing the system input masses ----

## check that the system inputs between the tubes aren't different
sys_input_compare <- imported_data %>% 
  select(trt, rep, ghop_fate, pred_prod, origin_dry, trt_added_mass) %>% 
  filter(trt != 'C') %>% 
  drop_na() %>% 
  unique() 

# summarize the system inputs data and make a table
sys_input_compare_summary <- sys_input_compare %>%
  group_by(trt) %>% 
  summarize(mean_origin_dry = mean(origin_dry), 
            se_origin_dry = se(origin_dry),
            ghop_fate = first(ghop_fate)) %>% 
  mutate(mean_origin_dry = mean_origin_dry*1000,
         se_origin_dry = se_origin_dry*1000,
         .keep = 'unused') %>% 
  select(trt, ghop_fate, everything())

## BAR PLOT with jitter
sys_input_compare_summary %>% 
  ggplot(aes(trt, mean_origin_dry, fill = ghop_fate)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_origin_dry - se_origin_dry, 
                     ymax = mean_origin_dry + se_origin_dry,
                     width = 0.15)) +
  geom_jitter(data = sys_input_compare, aes(trt, origin_dry*1000), width = 0.1)+
  scale_fill_manual(values = vir_4[1:3], name = 'Grasshopper fate') + 
  labs(#title = '\nOriginal animal input size',
    x = 'Treatment',
    y = 'Dry mass (mg)') +
  scale_x_discrete(labels=bar_x_labels_short) + 
  theme_yaya() + 
  theme(#plot.title = element_blank(),
    axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))
    # legend.position = 'none')

# my_ggsave(here::here('results/4_mass_system_input.png'), 5.5, 5.5)
```


```{r}

# table with summary stats for mass of system inputs
knitr::kable(
  sys_input_compare_summary,
  col.names = c("Treatment", "Prey fate", "Mean dry mass (mg)", "Standard error"),
  digits = 2)


mean_dry_carcass_mass <- sys_input_compare_summary %>% 
  filter(trt == 'G') %>% 
  select(mean_origin_dry)
```

The mean dry mass of locust carcasses is `r mean_dry_carcass_mass`


<br> <br> 

### Prey inputs to predators, analysis

This analysis is simply to ensure that the prey fed to each predator did not differ in origin size. We will use just remains (and not the waste treatment) to avoid duplication of the original dry prey mass (since they came from the same predator individuals).

Treatments included: G, MA, MR, WA, WW

```{r, echo=TRUE}
#---- Data analysis: stats for system inputs ----
## ANOVA for comparing the system ghop inputs per treatment
aov_prey_input <- aov(origin_dry ~ trt, filter(sys_input_compare, trt %in% c('G', 'MA', 'MR', 'WA', 'WW')))

summary(aov_prey_input)
```


Result: the mass of prey bodies entering each system is not different (p > 0.05)

Treatment did not have an effect on the initial grasshopper prey mass (i.e. all treatments received prey of similar mass). 



<br> <br> 

### Checking model assumptions (shapiro p = 0.002)

Model plots for assumption checks:

```{r, echo=TRUE}
par(mfrow=c(2,2))
plot(aov_prey_input)
ggqqplot(residuals(aov_prey_input))
```

1) Check for outliers

```{r echo=FALSE, message=FALSE, warning=FALSE}
## source from 
# https://www.datanovia.com/en/lessons/anova-in-r/#check-assumptions
## check for extreme outliers
sys_input_compare %>% 
  filter(trt %in% c('G', 'MA', 'MR', 'WA', 'WW')) %>% ## comment out if you want the whole dataset
  group_by(trt) %>% 
  rstatix::identify_outliers(origin_dry)

```

No outliers. 

2) Check for normality
The qq plot above looked not so normal, so we'll check with a Shapiro-Wilk test.

```{r echo=FALSE, message=FALSE, warning=FALSE}
## look at the normality
ggqqplot(residuals(aov_prey_input))

## shapiro wilks test for more statistically sound test of normality
rstatix::shapiro_test(residuals(aov_prey_input))
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
## can also do shapiro test on each group separately, but recommended only for n > 50
sys_input_compare %>% 
  filter(trt %in% c('G', 'MA', 'MR', 'WA', 'WW')) %>%
  group_by(trt) %>% 
  rstatix::shapiro_test(origin_dry)

## after running this we see it's the mantid products are that are non-normal (makes sense... there were big differences between the two feedings)
```

The residuals borderline significant with the top level comparisons (and from the graphic QQ plot they are not normal), meaning the assumption of normality is not met. So, we'll check for differences with the non-paramteric Kruskal-Wallis test as an alternative to a one-way ANOVA.

#### ___ Stats: Kruskal Wallis test

```{r echo=TRUE}
kruskal.test(origin_dry ~ trt, data = filter(sys_input_compare, trt %in% c('G', 'MA', 'MR', 'WA', 'WW')))
```

Great! Original grasshopper prey masses were not significantly different.

In my ESA talk, I compared grasshopper carcasses directly to mantid all and spider all using Kruskal-Wallis, so this is the right way forward.



<br><br>

## B) Quantity: predator products for soil microcosms

This is a plot of the mass of each animal necromass addition to soil microcosms. The statistical analyses will separate between the two levels (overall effect, and feeding strategy effect), but this figure is of all treatments. 

Units are in mg. 

```{r microcosm_inputs_summary}
#---- Figure: treatment inputs comparison -----
### now check that the treatment input is different
sys_input_compare %>%
  group_by(trt) %>% 
  summarize(mean_trt_added_mass = mean(trt_added_mass)*1000, 
            se_trt_added_mass = se(trt_added_mass)*1000,
            ghop_fate = first(ghop_fate)) %>% 
  ggplot(aes(trt, mean_trt_added_mass, fill = ghop_fate)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes(ymin = mean_trt_added_mass - se_trt_added_mass, 
                    ymax = mean_trt_added_mass + se_trt_added_mass,
                    width = 0.15)) +
  geom_jitter(data = sys_input_compare, aes(trt, trt_added_mass*1000), width = 0.1)+
  scale_fill_manual(values = vir_4[1:3], name = 'Grasshopper fate') + 
  labs(title = '\nAnimal necromass size added to microcosm',
       x = 'Treatment',
       y = 'Dry mass (mg)') +
  scale_x_discrete(labels=bar_x_labels_short) + 
  theme_yaya() + 
  theme(#plot.title = element_blank(),
    axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))
# legend.position = 'none')

# my_ggsave(here::here('results/4_mass_tube_input_jitter.png'), 7, 5.5)
```


Lets break it down into smaller questions/analyses.

### 1) The overall effect of predators

First we want to look at how predators, overall, affect the quantity and quality of animal necromass entering the soil microcosm. 

Treatments: G, MA, WA

#### Plot summary

Here's a barplot:

```{r}
#---- Figure: treatment inputs comparison -----
### now check that the treatment input is different
quant_prod_overall <- sys_input_compare %>%
  group_by(trt) %>% 
  filter(trt %in% c('G', 'MA', 'WA')) %>% 
  mutate(trt_added_mass_mg = trt_added_mass*1000)

quant_prod_overall %>% 
  summarize(mean_trt_added_mass = mean(trt_added_mass_mg), 
            se_trt_added_mass = se(trt_added_mass_mg),
            ghop_fate = first(ghop_fate)) %>% 
  ggplot(aes(trt, mean_trt_added_mass, fill = ghop_fate)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes(ymin = mean_trt_added_mass - se_trt_added_mass, 
                    ymax = mean_trt_added_mass + se_trt_added_mass,
                    width = 0.15)) +
  geom_jitter(data = quant_prod_overall, aes(trt, trt_added_mass*1000), width = 0.1)+
  scale_fill_manual(values = vir_4[1:3], name = 'Grasshopper fate') + 
  labs(title = '\nAnimal necromass size added to microcosm',
       x = '\nTreatment',
       y = 'Dry mass (mg)') +
  scale_x_discrete(labels=c('Prey carcass', 'Mantid all', 'Spider all')) +
  theme_yaya()
# legend.position = 'none')

# my_ggsave(here::here('results/4_mass_tube_input_jitter.png'), 7, 5.5)

```

#### Stats: ANOVA (shapiro p = 0.092)

```{r}
aov_prod_overall <- aov(trt_added_mass_mg ~ trt, quant_prod_overall)
summary(aov_prod_overall)
plot(aov_prod_overall)

quant_prod_overall %>% 
  rstatix::identify_outliers(trt_added_mass_mg)

# just the qq plot
ggqqplot(residuals(aov_prod_overall))
rstatix::shapiro_test(residuals(aov_prod_overall))

TukeyHSD(aov_prod_overall)
```
Shapiro Wilks p = 0.0916

At the moment, everything else is non-normal and requires Kruskal-Wallis, so even though this isn't "statistically significant" in terms of the test, maybe we stick to that? 

#### ***Stats: Kruskal Wallis

Due to borderline non-normality of the residuals in the standard ANOVA, we will run the Kruskal-Wallis test for top level treatments (carcass, mantid all, widow all):

```{r echo=TRUE}
kruskal.test(trt_added_mass_mg ~ trt, data = quant_prod_overall)
```

P < 0.05, so we reject the null hypothesis. Which treatments are different?

#### ***Post-hoc: Dunn's Test

```{r, echo=TRUE}
dunn.test(quant_prod_overall$trt_added_mass_mg, quant_prod_overall$trt, method = 'bonferroni')

(trt_added_dunn <- dunnTest(trt_added_mass ~ trt, 
                            sys_input_compare,
                            method = 'bonferroni'))
```

Carcass treatments were different from widow treatments, but mantids were not different from carcasses or spiders. 


### 2) Effect of feeding strategy on predator products

Next we want to see how the feeding strategy of predators affects the quantity of each type of animal necromass generated by foraging. 

Treatments: MR, ME, WW, WE 
WW = widow wrapped, which is the remains plus the wrapping silk

#### Plot summary
```{r}
quant_pred_feed <- sys_input_compare %>%
  group_by(trt) %>% 
  filter(trt %in% c('MR', 'ME', 'WW', 'WE')) %>% 
  mutate(trt_added_mass_mg = trt_added_mass*1000)

```

#### Stats: ANOVA (shapiro = 0.038) (don't use)

Run the ANOVA and check for normality and outliers.
```{r, echo = TRUE}
#---- Data analysis: stats for soil microcosm inputs ----
## ANOVA for comparing the system ghop inputs per treatment
aov_quant_feed <- aov(trt_added_mass_mg ~ ghop_fate * pred_prod, quant_pred_feed)

summary(aov_quant_feed)
# par(mfrow=c(2,2))
# plot(aov_quant_feed)

ggqqplot(residuals(aov_quant_feed))
rstatix::shapiro_test(residuals(aov_quant_feed))

quant_pred_feed %>% 
  group_by(trt) %>% 
  rstatix::identify_outliers(trt_added_mass_mg)
## no outliers
```
Shapiro wilks p = 0.038

Shapiro-Wilks analysis again suggests non-normality in the predator products, but it's a two-way ANOVA, which doesn't have a clear non-parametric equivalent...

But we'll give ART ANOVA a try!


#### ***Stats: ART ANOVA

Aligned Rank Transformation ANOVA: a non-parametric two-way factor test. 

```{r echo=TRUE}
art_quant_pred_feed <- art(trt_added_mass_mg ~ ghop_fate*pred_prod, quant_pred_feed)

anova(art_quant_pred_feed)
```

Huzzah it worked! There isn't a difference neither the product type or predator alone would predict amount of necromass produced, but the interaction between the two does (as we can see on the graph). 

```{r}
## this *would* be the code to test posthoc significance, but we dont need it in our case
# art.con(art_quant_pred_feed, "ghop_fate:pred_prod", interaction = TRUE, adjust = "bonferroni") %>% 
#   summary() %>% 
#   mutate(sig. = symnum(p.value, corr = FALSE, na = FALSE, 
#                        cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
#                        symbols = c("***", "**", "*", ".", " ")))
```


### 3) Other thoughts

----Future considerations?

It may be worth doing a regression analysis on the difference between the predator products (whether a chewing predator's waste is different from a sucking predator's remains and vice versa). Fixed effects, predator product, ghop fate; random effects, predator ID (but is this really important // the question I'm asking here? If no, stick to a simple ANOVA/the Kruskal-Wallis.)


----Old statistics from my seminar lecture 2021.04

For the seminar lecture, I ran a quick and dirty ANOVA, but this is not valid due to non-normality of residuals (as tested by the Shapiro-Wilks test). I was also concerned about the non-independence of the samples (since theoretically predator remains and predator wastes are inversely related, as they come from the same predator individuals). After talking to Shelby on 2021.09.25, I've decided to ignore it because it's pretty far removed from the samples taken, and even if I did correct for non-independence, it likely would not be driving the large differences seen between treatments here. 

```{r}
# rough and dirty: making the ANOVA model
aov_tube_inputs <- aov(trt_added_mass ~ trt, sys_input_compare) 
summary(aov_tube_inputs)

par(mfrow=c(2,2))
plot(aov_tube_inputs)

ggqqplot(resid(aov_tube_inputs))
shapiro.test(resid(aov_tube_inputs)) ## this is the dry mass of inputs. viraj says not too far from normal, probably ok.

## Data analysis: lm for tube inputs comparison by treatment-----
lm_tube_inputs <- lm(trt_added_mass ~ trt, sys_input_compare)
summary(lm_tube_inputs)
plot(lm_tube_inputs)


## Data analysis: lm for tube inputs comparison by treatment-----
lm_product_inputs0 <- lm(trt_added_mass ~ ghop_fate + pred_prod, sys_input_compare)
summary(lm_product_inputs0)

lm_product_inputs <- lm(trt_added_mass ~ ghop_fate * pred_prod, sys_input_compare)
summary(lm_product_inputs)
plot(lm_product_inputs)
alias(lm_product_inputs)


anova(lm_product_inputs0, lm_product_inputs)
```


----Trying out some weird things...

<br> 
Here is the same analysis, where I tried to use linear mixed models (I ran it to check for the effect of treatment mass on mineralization rates, but the random factorwas dropped on account of singularity).  


```{r}
# # ## mixed effect models: no random effect
# lm_sys_inputs <- lm(origin_dry ~ trt, data = sys_input_compare)
# knitr::kable(summary(lm_sys_inputs))
# 
# lm_sys_inputs %>%
#   broom::tidy() %>%
#   knitr::kable()
# 
# par(mfrow = c(2,2))
# plot(lm_sys_inputs)
```

A reminder, the significance of the intercept is that it is different from zero, which is not meaningful in this context (the model control treatment is "prey carcass").


## C) Quality of animal necromass

### 1) C and N data, all products summary + plots

Import all SIEL data for nutrient quality data from samples collected in the feeding assay.

```{r}
### import SIEL excel sheets
pp_siel_raw <- read_excel(here::here('data/SIEL data/YT1670-1_TotalCN_Rep, SIEL SO#1670 TRM.xls'), skip=2) %>%
  bind_rows(read_excel(here::here('data/SIEL data/YT1670-2_TotalCN_Rep, SIEL SO#1670 TRM.xls'), skip=2)) %>% 
  clean_names() %>% 
  remove_empty() %>% 
  filter(sample_id != 'spinach',
         sample_id != 'SF33F1') %>%  ### HUGE C and N values, some sort of entry error
  rename(mass_mg = weight_mg)

samp_data <- read_csv(here::here('data/CN_analysis_samples.csv')) %>% 
  clean_names() %>% 
  rename(ghop_fate = predator_type) %>% 
  filter(sample_type != 'silk')

samp_data[is.na(samp_data$ghop_fate),]$ghop_fate <- 'ghop'
samp_data[samp_data$sample_type ==  'feces',]$sample_type <- 'waste'
samp_data[samp_data$sample_type ==  'calib',]$sample_type <- 'carcass'


## created this key to be able to do ANOVA analyses later
pred_trt_key <- imported_data %>% 
  ungroup() %>% 
  select(trt, ghop_fate, pred_prod) %>% 
  unique() %>% 
  filter(!is.na(ghop_fate)) %>% 
  rename(sample_type = pred_prod) %>% 
  mutate(ghop_fate = as.character(ghop_fate),
         sample_type = as.character(sample_type))

# pred_trt_key[which(pred_trt_key$ghop_fate == 'carcass'),]$ghop_fate <- 'ghop'
pred_trt_key[which(pred_trt_key$sample_type == 'excreta'),]$sample_type <- 'waste'

## join SIEL data with sample meta data and the treatment key
prod_quality <- pp_siel_raw %>% 
  left_join(samp_data) %>% 
  left_join(pred_trt_key, by = c('ghop_fate', 'sample_type')) %>%
  mutate(pred_prod = paste(ghop_fate, sample_type)) %>% 
  rename(ghop_fate = ghop_fate) %>% 
  filter(sample_type != 'silk')


# prod_quality[is.na(prod_quality$sample_type),]$sample_type <- 'silk'
prod_quality[which(prod_quality$ghop_fate == 'ghop'),]$trt <- 'G'
# prod_quality[which(prod_quality$sample_type == 'silk'),]$trt <- 'WS'
```

##### Plots: distribution, mass summary, C:N ratio plot

Histograms of each variable:

```{r, fig.show="hold", out.width="50%"}
## check histograms of the product qualities
prod_quality %>% 
  ggplot(aes(total_percent_c)) +
  geom_histogram()
  # facet_grid(sample_type ~ ghop_fate)

prod_quality %>% 
  ggplot(aes(total_percent_n)) +
  geom_histogram()
  # facet_grid(sample_type ~ ghop_fate)

# nothing special here
prod_quality %>% 
  ggplot(aes(c_n_ratio)) +
  geom_histogram()
  # facet_grid(sample_type ~ ghop_fate)
```

Each treatment mass summarized in a table:

```{r}
## summarize predator products by treatment
(prod_summ <- prod_quality %>% 
  group_by(ghop_fate, sample_type) %>% 
  summarize(pred_prod = first(pred_prod),
            mean_c_n_ratio = mean(c_n_ratio),
            se_c_n_ratio = se(c_n_ratio),
            n = n()) %>% 
  ungroup() %>% 
  knitr::kable())
```

Plot of C:N ratios for prey carcasses and remains:

```{r}
prod_quality %>% 
  group_by(ghop_fate, sample_type) %>% 
  filter(trt %in% c('G', 'MR', 'WW')) %>% 
  ggplot(aes(trt, 
             c_n_ratio,
             fill = ghop_fate)) + 
  geom_boxplot(outlier.size = 3, outlier.shape = 23, outlier.fill = 'gray') + 
  scale_fill_viridis(discrete = TRUE) + 
  geom_jitter() + 
  expand_limits(y= 0) + 
  theme_yaya()
```

Plot of C:N ratios for predator products:

```{r}
prod_quality %>% 
  group_by(ghop_fate, sample_type) %>% 
  filter(trt %in% c('MR', 'ME', 'WW', 'WE')) %>% 
  ggplot(aes(trt, 
             c_n_ratio,
             fill = ghop_fate)) + 
  geom_boxplot(outlier.size = 3, outlier.shape = 23, outlier.fill = 'gray') + 
  scale_fill_viridis(discrete = TRUE) + 
  geom_jitter() + 
  expand_limits(y= 0) + 
  theme_yaya()
```


#### (a) Prey bodies, statistics

First, lets compare the qualities of the prey carcasses that are produced or left behind. 

Lets try a simple ANOVA, but since I think we'll have non-normality, lets run Shapiro-Wilks after as well.

---- Prey carcasses versus predator foraging remains 

```{r}
aov_quality_carcass <- aov(c_n_ratio ~ ghop_fate, filter(prod_quality, trt %in% c('G', 'MR', 'WW')))
summary(aov_quality_carcass)
plot(aov_quality_carcass)

## check for outliers
outliers_carcass <- prod_quality %>% 
  filter(trt %in% c('G', 'MR', 'WW')) %>% ## comment out if you want the whole dataset
  group_by(trt) %>% ## there are a couple extreme outliers if grouped by trt
    rstatix::identify_outliers(c_n_ratio)
# View(outliers_carcass) ## not that important for dissertation, maybe check on it for publication

## there are some outliers, but the removal of the extreme outliers doesn't change the qualitative nature of the analysis

rstatix::shapiro_test(residuals(aov_quality_carcass))
```

I ran the above tests twice: once with all the data points, and once without the extreme outliers (identified both visually and with rstatix::identify_outliers).

With all the data, there is some serious non-normality, so I ran a Kruskal-Wallis.

##### With outliers: Kruskal-Wallis test (maybe don't use?)

Due to non-normality of the residuals in the standard ANOVA, we will run the  Kruskal-Wallis test for the carcass-based treatments:

```{r echo=TRUE}
## kruskal-wallis for ALL treatments
kruskal.test(c_n_ratio ~ trt, filter(prod_quality, trt %in% c('G', 'MR', 'WW')))
```

We reject the null hypothesis. Which treatments are different?

###### Post-hoc: Dunn's Test (could be used to be consistent...)

```{r, echo=TRUE}
# dunn.test(prod_quality$c_n_ratio, prod_quality$trt, method = 'bonferroni')

dunnTest(c_n_ratio ~ trt,
         filter(prod_quality, trt %in% c('G', 'MR', 'WW')),
         method = 'bonferroni')
```

Ghop carcass did not differ from mantid remains but did differ from spider remains, while mantid remains did not differ from spider remains, and mantid excreta did not differ from spider excreta in quality. Every other comparison was significantly different.


##### Without outlier MR05F3

Repeating everything from the plot onward.

Plot of C:N ratios for grasshopper prey carcasses, without 'MR05F3'. It had an unusually low C *and* N (but less so), so it had a very very high C:N ratio. 

```{r}
qual_outliers <- tibble( trt = c('MR05F3')) ## if you change this, check next chunk statistics

## summarize predator products by treatment, without outliers or other treatments
prod_qual_clean <- prod_quality %>% 
  group_by(ghop_fate, sample_type) %>% 
  filter(trt %in% c('G', 'MR', 'WW')) %>% 
  anti_join(qual_outliers) 

prod_qual_clean %>% 
  ggplot(aes(trt, 
             c_n_ratio,
             fill = ghop_fate)) + 
  geom_boxplot(outlier.size = 3) + 
  scale_fill_viridis(discrete = TRUE) + 
  geom_jitter() + 
  expand_limits(y= 0) + 
  theme_yaya()

(prod_summ_clean <- prod_qual_clean %>% 
    group_by(ghop_fate, sample_type) %>% 
    summarize(pred_prod = first(pred_prod),
              mean_c_n_ratio = mean(c_n_ratio),
              se_c_n_ratio = se(c_n_ratio),
              n = n()) %>% 
    ungroup() %>% 
    knitr::kable())
```

###### ***Stats: ANOVA

```{r}
aov_quality_carcass_no_outliers <- aov(c_n_ratio ~ ghop_fate, filter(prod_quality, trt %in% c('G', 'MR', 'WW'), sample_id != 'MR05F3'))
summary(aov_quality_carcass_no_outliers)
plot(aov_quality_carcass_no_outliers)

## check for outliers
outliers_prod <- prod_quality %>% 
  filter(trt %in% c('G', 'MR', 'WW')) %>% ## comment out if you want the whole dataset
  anti_join(qual_outliers) %>% 
  group_by(trt) %>% ## there are a couple extreme outliers if grouped by trt
  rstatix::identify_outliers(c_n_ratio)
## not that important for dissertation, maybe check on it for publication

## there are some outliers, but the removal of the extreme outliers doesn't change the qualitative nature of the analysis

rstatix::shapiro_test(residuals(aov_quality_carcass_no_outliers))

## not checking shapiro wilks by groups because n > 50 and qqplot is preferred
ggqqplot(prod_qual_clean, 'c_n_ratio', facet.by = 'trt')

```

Without the one single extreme outlier, the data are quite normal. So we can stick to the original ANOVA. 

###### ***Post-hoc: Tukey HSD

```{r}
rstatix::tukey_hsd(aov_quality_carcass_no_outliers)
```

Results:
prey carcasses are not statistically significantly different from mantid remains (do not reject null)
prey carcasses ARE different from spider prey remains
same for mantid carcasses, different from spider prey remains

This makes sense because mantids leave behind parts of the prey body that are unadultered, while spiders are digesting the tissues extra-orally and leave behind remains lower in quality.


#### (b) Predator products, statistics

##### With outliers (shapiro p << 0.001)
```{r}
aov_pred_prod <- aov(c_n_ratio ~ ghop_fate * sample_type, filter(prod_quality, trt %in% c('MR', 'ME', 'WW', 'WE')))

summary(aov_pred_prod)
par(mfrow = c(2, 2))
plot(aov_pred_prod)

## check for outliers
outliers_pred_prod <- prod_quality %>% 
    filter(trt %in% c('MR', 'ME', 'WW', 'WE')) %>% 
    group_by(trt) %>% ## there are a couple extreme outliers if grouped by trt
    rstatix::identify_outliers(c_n_ratio)
# View(outliers_pred_prod) ## if you want to see whether the tubes are extreme

rstatix::shapiro_test(residuals(aov_pred_prod))
```

Shapiro test, very not normal. Is it because of the outliers?

##### Without outliers MR05F3 and SF06F1 (shapiro p = 0.133)

So lets try again, this time with removing the extreme outliers MR05F3 and SF06F1. SF06F1 was an extreme outlier (had an unusually low N), and was only 0.3mg in mass as compared to the other samples that were around 1mg.

Lets see the original boxplot again, without the extreme outliers:

```{r}
prod_quality %>% 
  group_by(ghop_fate, sample_type) %>% 
  filter(trt %in% c('MR', 'ME', 'WW', 'WE'),
         sample_id != 'SF06F1',
         sample_id != 'MR05F3') %>% 
  ggplot(aes(trt, 
             c_n_ratio,
             fill = ghop_fate)) + 
  geom_boxplot(outlier.size = 3, outlier.shape = 23, outlier.fill = 'gray') + 
  scale_fill_viridis(discrete = TRUE) + 
  geom_jitter() + 
  expand_limits(y= 0) + 
  theme_yaya()
```

###### ***Stats: ANOVA

```{r}
aov_pred_prod_clean <- aov(c_n_ratio ~ ghop_fate * sample_type, filter(prod_quality, trt %in% c('MR', 'ME', 'WW', 'WE'), sample_id != 'SF06F1', sample_id != 'MR05F3'))

summary(aov_pred_prod_clean)
par(mfrow = c(2, 2))
plot(aov_pred_prod_clean)

## check for outliers
outliers_pred_prod <- prod_quality %>% 
    filter(trt %in% c('MR', 'ME', 'WW', 'WE'),
           sample_id != 'SF06F1',
           sample_id != 'MR05F3') %>% 
    group_by(trt) %>% ## there are a couple extreme outliers if grouped by trt
    rstatix::identify_outliers(c_n_ratio)
# View(outliers_pred_prod) ## if you want to see whether the tubes are extreme

rstatix::shapiro_test(residuals(aov_pred_prod_clean))
```


###### ***Post-hoc: Tukey HSD

```{r}
rstatix::tukey_hsd(aov_pred_prod_clean) %>% 
  knitr::kable()
```

Results:
Mantid products were not different from spider products, but the quality (C:N) of remains was different from waste. And each of the four combinations was different from the other three. Specifically, any type of waste was much higher in quality (i.e. lower C:N) than any type of remains, spider wastes were slightly higher in quality than mantid wastes, and mantid wastes were slightly higher in quality than and spider wastes.



### 2) Protein content, summary

The protein analysis is limited because many of the samples were lost due to the USDA destroying them. We have some carcass samples and some spider remains samples analyzed for protein content using the Bradford and Lowry methods. 


#### Bradford protein
```{r}
protein_raw <- read_xlsx(here::here('data/protein analysis/Gideons protein summary.xlsx')) %>% 
  clean_names() %>% 
  rename(subsample_mg = mg_subsample_for_protein,
         lowry_protein_percent = lowry_protein_perc) %>% 
  select(-protein_vial_number)

protein_raw[which(protein_raw$sample_id == 'F2 S20'),]$sample_id <- 'F2 S20 PR'

protein_bradford <- protein_raw %>% 
  select(sample_id, bradford_protein_igg, bradford_protein_percent) %>% 
  separate(sample_id, c("feeding", "ghop_fate_id", "pred_prod")) %>% 
  mutate(ghop_fate = if_else(substr(ghop_fate_id, 1, 1)=='G', 'calib', 'spider')) %>% 
  mutate(pred_prod = if_else(is.na(pred_prod), 'carcass', 'remains')) 
```

Will get a warning about NAs (because some of the string only have one section and not three). 


This is boxplot and barplot of the same Bradford protein analysis.

```{r}
protein_bradford %>% 
  # group_by(ghop_fate, pred_prod) %>% 
  # summarize(bradford_se = se(bradford_protein_percent),
  #           bradford_avg = mean(bradford_protein_percent),
  #           bradford_n = n()) %>% 
  ggplot(aes(pred_prod,
             bradford_protein_percent,
             fill = ghop_fate)) + 
  geom_boxplot() + 
  geom_jitter() + 
  labs(title = '\nBradford protein analysis, carcasses vs spider remains') + 
  scale_fill_viridis(discrete = T) +
  expand_limits(y=0) +
  theme_yaya()


prod_colors <- viridis(4, option = "D")

protein_brad_summ <- protein_bradford %>% 
    group_by(ghop_fate, pred_prod) %>% 
    summarize(mean_bradford_protein_percent = mean(bradford_protein_percent),
              se_bradford_protein_percent = se(bradford_protein_percent),
              n = n()) %>% 
    ungroup()

# summary of protein data in a bar plot with error bars
protein_brad_summ %>% 
  ggplot(aes(ghop_fate, 
             mean_bradford_protein_percent, 
             fill = ghop_fate)) + 
  geom_bar(stat = 'identity',  position = position_dodge()) +
  geom_errorbar(aes(ymin = mean_bradford_protein_percent - se_bradford_protein_percent, 
                    ymax = mean_bradford_protein_percent + se_bradford_protein_percent),
                width = 0.15) +
  geom_jitter(data = protein_bradford,
              aes(ghop_fate,
                  bradford_protein_percent)) + 
  scale_fill_manual(values = c(viridis(4)[1], viridis(4)[3])) +
  # name='Input type',
  # labels = c('Grasshopper carcass', 'Spider prey remains')) + 
  scale_x_discrete(name = 'Grasshopper\nfate',
                   labels = c('Grasshopper\ncarcass', 'Spider\nprey remains')) +
  labs(title = '\n Protein content',
       x = 'Necromass type',
       y = '% protein (Bradford)',
       color = 'Treatment') +
  theme_yaya() + 
  theme(axis.title.x = element_blank(),
        legend.position = 'none')

# my_ggsave(here::here('results/protein_barplots_bradford.png'), 4, 4)

knitr::kable(protein_brad_summ)
```

You can see that the remains have 26% less protein than the protein found in the uneaten prey carcass. There is also far less variation. 


#### Lowry protein
```{r}
protein_lowry <- protein_raw %>% 
  select(sample_id, lowry_protein_igg, lowry_protein_percent) %>% 
  separate(sample_id, c("feeding", "ghop_fate_id", "pred_prod")) %>% 
  mutate(ghop_fate = if_else(substr(ghop_fate_id, 1, 1)=='G', 'calib', 'spider')) %>% 
  mutate(pred_prod = if_else(is.na(pred_prod), 'carcass', 'remains')) 
```

Will get a warning about NAs (because some of the string only have one section and not three). 

This is boxplot and barplot of the same Lowry protein analysis.

```{r}
protein_lowry %>% 
  # group_by(ghop_fate, pred_prod) %>% 
  # summarize(lowry_se = se(lowry_protein_percent),
  #           lowry_avg = mean(lowry_protein_percent),
  #           lowry_n = n()) %>% 
  ggplot(aes(pred_prod,
             lowry_protein_percent,
             fill = ghop_fate)) + 
  geom_boxplot() + 
  geom_jitter() + 
  labs(title = '\nlowry protein analysis, carcasses vs spider remains') + 
  scale_fill_viridis(discrete = T) +
  expand_limits(y=0) +
  theme_yaya()

prod_colors <- viridis(4, option = "D")

protein_lowry_summ <- protein_lowry %>% 
    group_by(ghop_fate, pred_prod) %>% 
    summarize(mean_lowry_protein_percent = mean(lowry_protein_percent),
              se_lowry_protein_percent = se(lowry_protein_percent),
              n = n()) %>% 
    ungroup()

# summary of protein data in a bar plot with error bars
protein_lowry_summ %>% 
  ggplot(aes(ghop_fate, 
             mean_lowry_protein_percent, 
             fill = ghop_fate)) + 
  geom_bar(stat = 'identity',  position = position_dodge()) +
  geom_errorbar(aes(ymin = mean_lowry_protein_percent - se_lowry_protein_percent, 
                    ymax = mean_lowry_protein_percent + se_lowry_protein_percent),
                width = 0.15) +
  geom_jitter(data = protein_lowry,
              aes(ghop_fate,
                  lowry_protein_percent)) + 
  scale_fill_manual(values = c(viridis(4)[1], viridis(4)[3])) +
  # name='Input type',
  # labels = c('Grasshopper carcass', 'Spider prey remains')) + 
  scale_x_discrete(name = 'Grasshopper\nfate',
                   labels = c('Grasshopper\ncarcass', 'Spider\nprey remains')) +
  labs(title = '\n Protein content',
       x = 'Necromass type',
       y = '% protein (lowry)',
       color = 'Treatment') +
  theme_yaya() + 
  theme(axis.title.x = element_blank(),
        legend.position = 'none')

# my_ggsave(here::here('results/protein_barplots_lowry.png'), 4, 4)

knitr::kable(protein_lowry_summ)
```

From the Lowry analysis, we see less of a reduction in the percent protein (15% less protein in remains than in carcasses). Bradford protein analysis had lower percent protein values for both sample types, but the relationship between the two is still the same. 


#### Stats: Bradford protein, Welch's t-test

This is the one I'll use in the paper, since Bradford protein assays are more widely reported. 

We will check the variances of the two groups to decide whether it will be a t-test or a Welch's t-test.

```{r echo=FALSE}
protein_bradford %>% 
  group_by(ghop_fate) %>% 
  summarize(n = n(),
            mean = mean(bradford_protein_percent))

brad1 <- subset(protein_bradford, ghop_fate == 'calib')
brad2 <- subset(protein_bradford, ghop_fate == 'spider')
var.test(brad1$bradford_protein_percent, brad2$bradford_protein_percent)
```

var test p << 0.001

Since the variances of the two groups are unequal, we can try Welch's t-test for unequal variances.  But first we need to check for the normality of each of the samples.
(from stackexchange: The t-test is invalid for small samples from non-normal distributions, but it is valid for large samples from non-normal distributions. [where large is likely ])

```{r}
rstatix::shapiro_test(brad1$bradford_protein_percent)
rstatix::shapiro_test(brad2$bradford_protein_percent)
```


```{r}
t.test(bradford_protein_percent ~ ghop_fate, data = protein_bradford,
       var.equal = FALSE, conf.level = 0.95)
```

Welch's t-test for two samples with unequal variances suggest we reject the null hypothesis that these two groups are the same. But I'm concerned about the unequivalent sample sizes, and assumptions about normality. So, lets do a Wilcoxon-Mann-Whitney test.

#### ***Stats: Bradford protein, Wilcoxon test

```{r}
wilcox.test(brad1$bradford_protein_percent, brad2$bradford_protein_percent)
```

Wilcoxon signed rank test: p << 0.001


#.

# __Necrobiome necromass addition? __

Maybe a section on the inferred amounts of biomass/ total C calculated to have been added to each microcosm?

#.

# Necrobiome function

First look at the daily dynamics of each tube. For this, we need to include the cumulative values.

```{r}
## graph of phase 1 cumulative C, scaled to biomass

cumul_data <- imported_data %>% 
  mutate(ghop_fate= first(ghop_fate),
         origin_dry = first(origin_dry),
         trt_added_mass = first(trt_added_mass),
         cumul_c_gross = cumsum(infer_tube_total_daily),
         infer_daily_scaled = infer_tube_total_daily / trt_added_mass,
         cumul_c_daily_scaled = cumsum(infer_daily_scaled)) %>% 
  arrange(tube_id, exp_count)

```

This is an interactive plotly to looking at the daily, individual tube dynamics

```{r}
## This chunk makes a plotly object from the ggplot to explore raw daily dynamic data from each individual tube

dyn_daily <- cumul_data %>% 
  group_by(trt, rep) %>% 
  # filter(group_compute == 1) %>% 
  # filter(trt == 'WR') %>%
  # View()
  ggplot(aes(x = exp_count, y = infer_tube_total_daily, 
             group = interaction(trt, rep))) +
  geom_line(aes(color = trt)) + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized daily by each tube',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_daily)
```


```{r}
## This chunk makes a plotly object from the ggplot to explore dynamic CUMULATIVE C data from each individual tube

dyn_cumul <- cumul_data %>% 
  group_by(trt, rep) %>% 
  # filter(trt == 'WR') %>% 
  # View()
  ggplot(aes(x = exp_count, y = cumul_c_gross, 
             group = interaction(trt, rep))) +
  geom_line(aes(color = trt)) + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul) 
```


## 1) Overall effect of predators on necrobiome function

So lets look more closely at the treatments that compare the effect of predators on the decomposition of anim  ### All phases, cumulative

### A) All phases, cumulative dynamic plot

```{r}
data_overall_all <- cumul_data %>%
  group_by(trt, rep) %>% ## this is a more flexible way to group by tube
  filter(group_compute == 1) %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily)) %>%
  # this is actually a duplicate column of cumulative values
  ungroup() 

dyn_cumul_q1_all <- data_overall_all %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = ghop_fate)) +
  # geom_point(aes(shape = pred_prod)) +
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, all phases',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q1_all)
```

#### End of all phases 

Here are the values at the end of the experiment:

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q1_all <- data_overall_all %>% 
  filter(exp_count == max(exp_count))

end_cumul_q1_all %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = ghop_fate)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q1_all, aes(x = trt, y= cumul_c_gross_phase, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('carcass', 'mantid, all', 'spider, all', 'control')) + 
  labs(title = 'C mineralized cumulatively by treatment, all phases',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

```

##### ***Stats: ANOVA (shapiro p = 0.670) (ANOVA p << 0.001, F = 9.029)

First try an ANOVA, and check for normality.

```{r}
outliers_q1_all <- end_cumul_q1_all %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_gross_phase)
# View(outliers_q1_all)

aov_overall_all <- aov(cumul_c_gross_phase ~ trt, end_cumul_q1_all)

summary(aov_overall_all)

ggqqplot(residuals(aov_overall_all))
rstatix::shapiro_test(residuals(aov_overall_all))
```

Shapiro wilks p = 0.670

So actually, the data from all phases are normal than phase 1, and we see that treatment *does* have an effect. Which treatments?


###### ***Post-hoc: Tukey HSD

```{r}
rstatix::tukey_hsd(aov_overall_all) %>% 
  arrange(group1) %>% 
  knitr::kable()
```

---Results: (originally written when this section was after phase 1 and phase 2 results) 

Control and prey carcass treatments are very different (p << 0.001).
Controls are not different from the two predator treatments
The two predator treatments don't differ from one another
But the carcass treatment differs mantid all and spider all.

---Discussion:

This makes some sense. The overall effect of the predators has primarily do to with the C mineralized in phase 1. In phase 2 where we tested the legacy effect of animal necromass added in phase 1, we saw all treatments receiving animal necromass had reduced function (lower than control tubes).

Some possible explanations: 
--we saw in some quality levels in chapter 1, that function was depressed across various soils
--these were desert soils, which may have a more restricted range of ability (due to their more extreme circumstances)

---Things to consider in the future:
Maybe look at the amount of C added to each tube, and consider scaling the C response as a fraction of the total C available in each tube. 


### B) Phase 1... animal necromass decomp

The overall effect of predator of direct decomposition

###_ Phase 1 dynamic plots

This is a plot of the CO2 respiration of each treatment during phase 1.

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 1
data_overall_p1 <- cumul_data %>%
  group_by(trt, rep) %>%
  filter(phase == 1,
         group_compute == 1) %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily)) %>%
  ungroup()
  
# pick <- function(condition){
#   function(d) d %>% filter(!!enquo(condition))
# }

dyn_cumul_q1_p1 <- data_overall_p1 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            phase_count = first(phase_count)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt)) +
  # geom_point(data = pick(~phase_count !is.na), aes(shape = trt)) +
    # geom_point(aes(color = phase_count))
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, phase 1 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q1_p1)
```


#### End of phase 1 

The analyses we'll do will be on the statistics at the end of each phase and over the entire experiment.  Here are the data for phase 1.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q1_p1 <- data_overall_p1 %>% 
  filter(exp_count == max(exp_count))

end_cumul_q1_p1 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = ghop_fate)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q1_p1, aes(x = trt, y= cumul_c_gross_phase, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('carcass', 'mantid, all', 'spider, all', 'control')) +
  labs(title = 'C mineralized cumulatively by treatment, phase 1 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

```

##### ___Stats: ANOVA (shapiro = 0.001)

First I tried an  ANOVA, and checked for normality since I figure it won't be very normal.

```{r}
outliers_q1_p1 <- end_cumul_q1_p1 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_gross_phase)
# View(outliers_q1_p1)

# q1_p1_outliers <- tibble(tube_id = c('G.11', 'G.12'))

aov_overall_p1 <- aov(cumul_c_gross_phase ~ trt,
                      # anti_join(end_cumul_q1_p1, q1_p1_outliers))
                      end_cumul_q1_p1)

summary(aov_overall_p1)

ggqqplot(residuals(aov_overall_p1))
rstatix::shapiro_test(residuals(aov_overall_p1))
```

Shapiro wilks p = 0.001

##### Posthoc: Tukey's HSD
```{r}
rstatix::tukey_hsd(aov_overall_p1)
```


##### ___Stats: Kruskal-Wallis

```{r echo=TRUE}
kruskal.test(cumul_c_gross_phase ~ trt, end_cumul_q1_p1)
```

Kruskal-Wallis p << 0.001. 

##### ___Stats: Dunn Test
```{r, echo=TRUE}
(dunn_q1_p1 <- dunnTest(cumul_c_gross_phase ~ trt, 
                            end_cumul_q1_p1,
                            method = 'bonferroni'))
```

Control is different from the rest, as are the prey carcass treatments. Mantid all and spider all however did not differ. 


### C) Phase 2... plant necromass decomp

Here we want to compare how the decomposition of 500mg of plant litter is affected by the phase 1 deposition of animal necromass.

#### Phase 2 dynamic plots

This is comparing the overall effect of predators in phase 2. 

Treatments: G, MA, WA

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 2
data_overall_p2 <- cumul_data %>%
  group_by(trt, rep) %>%
  filter(phase == 2,
         group_compute == 1) %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily)) %>%
  ungroup() 

dyn_cumul_q1_p2 <- data_overall_p2 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = ghop_fate)) +
  # geom_point(aes(shape = pred_prod)) + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, phase 2 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q1_p2)
```

#### End of phase 2 

The analyses we'll do will be on the statistics at the end of each phase and over the entire experiment. Here are the data for phase 2.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q1_p2 <- data_overall_p2 %>% 
  filter(exp_count == max(exp_count))

end_cumul_q1_p2 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = ghop_fate)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q1_p2, aes(x = trt, y= cumul_c_gross_phase, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('carcass', 'mantid, all', 'spider, all', 'control')) + 
  labs(title = 'C mineralized cumulatively by treatment, phase 2 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

```

##### ***Stats: ANOVA (shapiro p = 0.798) (ANOVA p < 0.01, F = 5.539 )

First try an ANOVA, and check for normality.

```{r}
outliers_q1_p2 <- end_cumul_q1_p2 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_gross_phase)
# View(outliers_q1_p2)

aov_overall_p2 <- aov(cumul_c_gross_phase ~ trt, end_cumul_q1_p2)

summary(aov_overall_p2)
par(mfrow = c(2,2))
plot(aov_overall_p2)

rstatix::shapiro_test(residuals(aov_overall_p2))
```

Shapiro wilks p = 0.798

So actually, the data from phase 2 are more normal than phase 1, and if we use a standard ANOVA we see that treatment *does* have an effect. Which treatments?


##### ***Post-hoc: Tukey HSD

```{r}
rstatix::tukey_hsd(aov_overall_p2) %>% 
  arrange(group2) %>% 
  knitr::kable()
```

Results:
Control tubes were different from all other treatments (and much higher). Prey carcasses didnt differ from mantid all or spider all, and vice versa. 


#. 

## 2) Potential interactive effects of predator foraging by-products

Now lets look at the effect of predator products separately, and whether they interact to increase necrobiome function when occuring together.

Calculate the difference from control in each tube, and then add the two separated predator treatments together.

```{r}

calc_diff <- cumul_data %>%
  left_join(select(ctrl_data, c('exp_count', 'ctrl_daily_mean', 'ctrl_daily_se')), by = c('exp_count')) %>% 
  group_by(trt, rep) %>% 
  arrange(exp_count) %>% 
  mutate(tube_daily_diff = infer_tube_total_daily - ctrl_daily_mean) %>% 
  # infer_diff_scaled = tube_daily_diff / trt_added_mass) 
  ungroup()
         

calc_mantid <- calc_diff %>% 
  filter(ghop_fate == 'mantid',
         pred_prod != 'all') %>% 
  group_by(ghop_fate, rep, exp_count) %>% 
  summarize(tube_daily_diff = sum(tube_daily_diff),
            origin_dry = first(origin_dry),
            computed_added_mass = sum(trt_added_mass)) %>% 
  mutate(trt = factor('MC'),
         pred_prod = factor('computed'),
         tube_id = paste0(trt, '.', formatC(rep, width=2, flag="0")))
  
calc_spider <- calc_diff %>% 
  filter(ghop_fate == 'spider',
         pred_prod != 'all') %>% 
  group_by(ghop_fate, rep, exp_count) %>% 
  summarize(tube_daily_diff = sum(tube_daily_diff),
            origin_dry = first(origin_dry),
            computed_added_mass = sum(trt_added_mass)) %>% 
  mutate(trt = factor('WC'),
         pred_prod = factor('computed'),
         tube_id = paste0(trt, '.', formatC(rep, width=2, flag="0")))

irga_meta_ctrl <- cumul_data %>% 
  ungroup() %>% 
  select(phase, phase_count, exp_count) %>% 
  unique() %>% 
  left_join(select(ctrl_data, c('exp_count', 'ctrl_daily_mean', 'ctrl_daily_se')), by = c('exp_count'))

computed_pred_data <- bind_rows(calc_mantid, calc_spider) %>% 
  left_join(irga_meta_ctrl) %>% 
  bind_rows(filter(calc_diff, trt %in% c('MA', 'WA'))) %>% 
  mutate(pred_prod = factor(pred_prod, levels = c('none', 'all', 'computed', 'remains', 'excreta')))

```

### A) All phases, cumulative

#### All phases, cumulative dynamic plot

This plot may be left out, because the final results don't seem to make a whole lot of sense when considered together...

```{r}
data_computed_all <- computed_pred_data %>%
  group_by(trt, rep) %>% ## this is a more flexible way to group by tube
  mutate(cumul_c_diff_phase = cumsum(tube_daily_diff)) %>%
  ungroup() 

dyn_diff_q2_all <- data_computed_all %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod),
            phase_count = first(phase_count)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_diff_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = pred_prod)) +
  # geom_point(aes(shape = pred_prod)) +
  geom_hline(aes(yintercept = 0), color="gray", size = 1.5, linetype = "dashed") + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively as the difference from control, all phases',
       x = 'Incubation Day',
       y = 'C mineralization (mg)') +
  theme_dyn

ggplotly(dyn_diff_q2_all)
```

##### Dynamic diff plot to compare all treatments

Lets take a quick look at how this compares to other treatments (difference relative to control)

```{r}
computed_pred_compare <- bind_rows(calc_mantid, calc_spider) %>% 
  left_join(irga_meta_ctrl) %>% 
  bind_rows(filter(calc_diff, trt %in% c('MA', 'WA', 'MR', 'ME', 'WW', 'WE'))) %>% 
  mutate(pred_prod = factor(pred_prod, levels = c('none', 'all', 'computed', 'remains', 'excreta')))

data_computed_all_compare <- computed_pred_compare %>%
  group_by(trt, rep) %>% ## this is a more flexible way to group by tube
  mutate(cumul_c_diff_phase = cumsum(tube_daily_diff)) %>%
  ungroup() 

dyn_diff_q2_all_compare <- data_computed_all_compare %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod),
            phase_count = first(phase_count)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_diff_p, 
             group = ghop_fate)) +
  geom_line(aes(color = trt,
                linetype = pred_prod)) +
  # geom_point(aes(shape = pred_prod)) +
  geom_hline(aes(yintercept = 0), color="gray", size = 1.5, linetype = "dashed") + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively as the difference from control, all phases',
       x = 'Incubation Day',
       y = 'C mineralization (mg)') +
  theme_dyn

ggplotly(dyn_diff_q2_all_compare)

```



#### End of all phases 

Here are the computed values at the end of the experiment:

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q2_all <- data_computed_all %>% 
  filter(exp_count == max(exp_count))

end_cumul_q2_all %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_diff_p, 
             fill = trt)) +
  geom_col(position = 'dodge',
           color = 'black') +
  geom_errorbar(aes( ymin = mean_cumul_diff_p - se_cumul_diff_p, 
                     ymax = mean_cumul_diff_p + se_cumul_diff_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q2_all, 
              aes(x = trt, y= cumul_c_diff_phase),
              width = 0.2) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('mantid computed', 'spider computed', 'mantid all', 'spider all')) +
  labs(title = 'C mineralized cumulatively as difference from control, all phases',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  # facet_grid(. ~ ghop_fate) + 
  theme_dyn

```

##### ***Stats: ANOVA (shapiro p = 0.142) (ANOVA p > 0.05, pred prod F = 1.614)

First try an ANOVA, and check for normality.

```{r}
outliers_q2_all <- end_cumul_q2_all %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_diff_phase)
# View(outliers_q2_all)

aov_computed_all <- aov(cumul_c_diff_phase ~ ghop_fate * pred_prod, end_cumul_q2_all)

summary(aov_computed_all)

ggqqplot(residuals(aov_computed_all))

rstatix::shapiro_test(residuals(aov_computed_all))
```


--- Results

Looking cumulatively, there is no difference between computing the predator products and them combined in the same tube. 

When broken down between each phase, we see that in the first phase the computed treatments have higher respiration rates than the products all together, while in phase 2 the reverse is true. During decomposition of plant necromass, 


(Visual) Compared to the separate predator products:
Mantid all microcoasms

--- Discussion

The combining of predator products in the same 



### B) Phase 1... computed predator products

```{r}
data_computed_p1 <- computed_pred_data %>%
  group_by(trt, rep) %>%
  filter(phase == 1) %>% 
  mutate(cumul_c_diff_phase = cumsum(tube_daily_diff)) %>%
  ungroup()
  
dyn_diff_q2_p1 <- data_computed_p1 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod),
            phase_count = first(phase_count)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_diff_p)) +
  geom_line(aes(color = trt,
                linetype = pred_prod)) +
  # geom_point(data = pick(~phase_count !is.na), aes(shape = trt)) +
    # geom_point(aes(color = phase_count))
  geom_hline(aes(yintercept = 0), color="gray", size = 1.5, linetype = "dashed") + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively as the difference from control, phase 1 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_diff_q2_p1)
```


#### End of phase 1 

Here are the data for phase 1.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_diff_q2_p1 <- data_computed_p1 %>% 
  filter(exp_count == max(exp_count))

end_diff_q2_p1 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_diff_p, 
             fill = trt)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_diff_p - se_cumul_diff_p, 
                     ymax = mean_cumul_diff_p + se_cumul_diff_p,
                     width = 0.15)) +
  geom_jitter(data = end_diff_q2_p1, aes(x = trt, y= cumul_c_diff_phase, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  # scale_x_discrete(labels = c('carcass', 'mantid, all', 'spider, all', 'control')) + 
  labs(title = 'C mineralized cumulatively by treatment, phase 1 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn
```


##### ___Stats: ANOVA (shapiro = 0.412) (ANOVA p = 0.865)

First I tried an  ANOVA, and checked for normality.

```{r}
outliers_q2_p1 <- end_diff_q2_p1 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_diff_phase)
# View(outliers_q2_p1)

aov_computed_p1 <- aov(cumul_c_diff_phase ~ trt, end_diff_q2_p1)

summary(aov_computed_p1)
par(mfrow = c(2,2))
plot(aov_computed_p1)

rstatix::shapiro_test(residuals(aov_computed_p1))
```

Shapiro wilks p = 0.412. Looks ok, so we can consider keeping it.

##### ___Stats:, Kruskal-Wallis p = 0.958

```{r echo=TRUE}
kruskal.test(cumul_c_diff_phase ~ trt, end_diff_q2_p1)
```

Kruskal-Wallis p = 0.958.

No effect of treatment / predator product addition on C mineralization in the first phase. 


### C) Phase 2... plots

```{r}
data_computed_p2 <- computed_pred_data %>%
  group_by(trt, rep) %>%
  filter(phase == 2) %>% 
  mutate(cumul_c_diff_phase = cumsum(tube_daily_diff)) %>%
  select(trt, rep, exp_count, infer_tube_total_daily, ctrl_daily_mean, tube_daily_diff, cumul_c_diff_phase, everything()) %>% 
  ungroup()
  
dyn_diff_q2_p2 <- data_computed_p2 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod),
            phase_count = first(phase_count),
            mean_origin_dry = mean(origin_dry)) %>% 
  # View()
  ggplot(aes(x = exp_count, 
             y = mean_cumul_diff_p, 
             label = mean_origin_dry)) +
  geom_line(aes(color = trt,
                linetype = pred_prod)) +
  # geom_point(data = pick(~phase_count !is.na), aes(shape = trt)) +
    # geom_point(aes(color = phase_count))
  geom_hline(aes(yintercept = 0), color="gray", size = 1.5, linetype = "dashed") + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively as the difference from control, phase 2 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_diff_q2_p2)
```


#### End of phase 2 

Here are the data for phase 2.

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 2
end_diff_q2_p2 <- data_computed_p2 %>% 
  filter(exp_count == max(exp_count))

end_diff_q2_p2 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_diff_p = mean(cumul_c_diff_phase),
            se_cumul_diff_p = se(cumul_c_diff_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_diff_p, 
             fill = trt)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_diff_p - se_cumul_diff_p, 
                     ymax = mean_cumul_diff_p + se_cumul_diff_p,
                     width = 0.15)) +
  geom_jitter(data = end_diff_q2_p2, aes(x = trt, y= cumul_c_diff_phase, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  # scale_x_discrete(labels = c('carcass', 'mantid, all', 'spider, all', 'control')) + 
  labs(title = 'C mineralized cumulatively by treatment, phase 2 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn
```


##### ___Stats: ANOVA (shapiro = 0.615) (ANOVA pred prod p = 0.002)

First I tried an ANOVA, and checked for normality.

```{r}
outliers_q2_p2 <- end_diff_q2_p2 %>% 
  group_by(trt) %>% ## there are a couple extreme outliers if grouped by trt
  rstatix::identify_outliers(cumul_c_diff_phase)
# View(outliers_q2_p2)
## no extreme outliers in this dataset

aov_computed_p2 <- aov(cumul_c_diff_phase ~ ghop_fate * pred_prod, end_diff_q2_p2)
summary(aov_computed_p2)

# par(mfrow = c(2,2))
# plot(aov_computed_p2)
ggqqplot(residuals(aov_computed_p2))
rstatix::shapiro_test(residuals(aov_computed_p2))
```
Shapiro wilks p = 0.615

##### Posthoc, Tukey's

```{r}
rstatix::tukey_hsd(aov_computed_p2) %>% 
  knitr::kable()
```


Looks pretty normal... but I'm not sure an ANOVA would hold up in other datasets. Anyway, the results of the ANOVA + posthoc with the two factors and the interaction term suggest there's a difference between the predator products, but not between the predator types.

There is also one interaction effect, where mantid all is different from spider computed (this isn't very meaningful). 

##### Stats:, Kruskal-Wallis p = 0.041

```{r echo=TRUE}
kruskal.test(cumul_c_diff_phase ~ trt, end_diff_q2_p2)
```

The Kruskal wallis test appears to have the same p-statistic as the simple ANOVA (formula with cumul_c_diff_phase ~ trt). This makes me suspicious... Anyway it doesn't have the two factorial terms. 


##### ___Stats: ART ANOVA (pred prod p = 0.005, F = 8.842)

I'm going to give ART ANOVA a try here also, since the data seem relatively normal, but all the previous IRGA data doesn't seem particularly normal. 

Aligned Rank Transformation ANOVA: a non-parametric two-way factor test. 

```{r echo=TRUE}
art_computed_p2 <- art(cumul_c_diff_phase ~ ghop_fate * pred_prod, end_diff_q2_p2)

anova(art_computed_p2)
```

pred_prod p = 0.0047 (this p value is )

ART ANOVA suggests there is a effect of combining the predator products over having them in one tube. Lets check the posthoc.

##### Posthoc: estimate = 11.3 for all - computed comparison)

```{r}
art.con(art_computed_p2, "pred_prod", interaction = T, adjust = "bonferroni") %>%
  summary() %>%
  mutate(sig. = symnum(p.value, corr = FALSE, na = FALSE,
                       cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                       symbols = c("***", "**", "*", ".", " ")))
```

---Results

There was no difference in the fate of the grasshoppers (i.e. whether it was eaten by a chewing vs sucking predator), but there was an effect of computed predator products treatment (i.e. computed values were *lower* in CO2 respiration rate than the treatments receiving all predator foraging by-products in the same tube. 

CO2 respiration rate than the computed sum of the respiration rate of each of the two products in separate microcosms).


---Discussion

There appears to be a legacy effect, that the addition of animal necromass depresses the function of the necrobiome. This was surprising, because we expected to see improved function with the addition of high quality necromass. 

The addition of both products into each microcosm resulted in higher function than each of the products alone. It was also the case that the computer addition of 

However these soils are from the desert (where the two predators are found in the same environment), and it may be true that this necrobiome has more limited range of function.


#.
#.

## 3) Effect of predator feeding strategy on necrobiome function

### --UNSCALED---

So lets look more closely at the treatments that compare the effect of predators on the decomposition of animal necromass.

### A) All phases

#### *) All phases dynamic plot

```{r}
data_strat_unscaled_all <- cumul_data %>%
  group_by(trt, rep) %>% ## this is a more flexible way to group by tube
  filter(group_compute == 2) %>% # for all the predator product treatments
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily)) %>%
  # this is actually a duplicate column of cumulative values
  ungroup() 

dyn_cumul_q3_un_all <- data_strat_unscaled_all %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = ghop_fate)) +
  # geom_point(aes(shape = pred_prod)) +
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, all phases',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q3_un_all)
```

#### End of all phases 

Here are the predator product values at the end of the experiment:

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q3_un_all <- data_strat_unscaled_all %>% 
  filter(exp_count == max(exp_count))

end_cumul_q3_un_all %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = trt,
             label = pred_prod),
         group = interaction(ghop_fate, pred_prod)) + 
  geom_col(position = 'dodge', color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q3_un_all, 
              aes(x = trt, y= cumul_c_gross_phase, group = ghop_fate),
              width = 0.2) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('mantid remains', 'mantid waste', 'spider remains', 'spider waste')) +
  labs(title = 'C mineralized cumulatively by treatment, all phases',
       x = '\nTreatment',
       y = 'C mineralization (mg)\n',
       color = 'Treatment') +
  theme_dyn

```

##### ***Stats: ANOVA (shapiro p = 0.280) (ANOVA pred_prod p < 0.001, F = 13.711)

First try an ANOVA, and check for normality.

```{r}
outliers_q3_un_all <- end_cumul_q3_un_all %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_gross_phase)
# View(outliers_q3_un_all)

aov_strategy_all <- aov(cumul_c_gross_phase ~ ghop_fate * pred_prod, end_cumul_q3_un_all)

summary(aov_strategy_all)

ggqqplot(residuals(aov_strategy_all))
rstatix::shapiro_test(residuals(aov_strategy_all))
```

ANOVA significance

pred prod p = 0.001
ghop_fate * pred_prod p = 0.032


##### ***Post-hoc: Tukey HSD

```{r}
rstatix::tukey_hsd(aov_strategy_all) %>% 
  knitr::kable()
```

---Results
Over the entire experiment, predator products were significantly different from one another (remains were different from excreta). 

For specific interactions, spider excreta had the lowest respiration rates and differed significantly from mantid remains and spider remains (although there was no difference between mantid excreta and spider excreta). 


--Discussion
Here we wanted to test whether the feeding strategy of a predator would result in qualitatively different responses in necrobiome function. Although the overall effect of the predator was not significant, spider wastes resulted in a much lower response than other treatments. Now lets look at phases 1 and 2 to see whether the effect is from the direct decomposition of the animal necromass, or the indirect functional change in plant necrobiomass decomposition. 



### B) Phase 1... overall effect of predator of direct decomposition

#### Phase 1 dynamic plots

This is a plot of the CO2 respiration of each relevant treatment during phase 1.

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 1
data_strat_unscaled_p1 <- cumul_data %>%
  group_by(trt, rep) %>%
  filter(phase == 1,
         group_compute == 2) %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily)) %>%
  ungroup()
  
dyn_cumul_q3_un_p1 <- data_strat_unscaled_p1 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            phase_count = first(phase_count)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt)) +
  # geom_point(data = pick(~phase_count !is.na), aes(shape = trt)) +
    # geom_point(aes(color = phase_count))
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, phase 1 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q3_un_p1)
```


#### End of phase 1 

The analyses we'll do will be on the statistics at the end of each phase and over the entire experiment.  Here are the data for phase 1.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q3_un_p1 <- data_strat_unscaled_p1 %>% 
  filter(exp_count == max(exp_count))

end_cumul_q3_un_p1 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = trt)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q3_un_p1, 
              aes(x = trt, y= cumul_c_gross_phase, group = ghop_fate),
              width = 0.2) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('mantid remains', 'mantid waste', 'spider remains', 'spider waste')) +
  labs(title = 'C mineralized cumulatively by treatment, phase 1 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn
```


This table summarizes the mean mass of each treatment that was added to the soil microcosms:

```{r}
end_cumul_q3_un_p1 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod),
            mean_trt_added_mass = mean(trt_added_mass)) %>% 
  knitr::kable()
```


#### Trt added mass vs C mineralized

Just to understand the effect of the amount of necromass added, here's a plot of the mass added to each microcosm against the C mineralization of the phase.

```{r}
## see if the trt added mass drove this effect
end_cumul_q3_un_p1 %>% 
  ggplot(aes(x = trt_added_mass, # *1000, # can use this if you want two axes to be same metric
             y = cumul_c_gross_phase,
             group = trt)) + 
  geom_point(aes(color = trt)) +
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by microcosm added mass, phase 2 only',
       x = 'Original product mass (mg)',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

regress_trt_add <- lm(cumul_c_gross_phase ~ trt_added_mass * trt, # pred_prod,
                      end_cumul_q3_un_p1)
summary(regress_trt_add)

```


##### Stats: ANOVA (shapiro = 0.024) (ghop_fate:pred_prod p = 0.001 F = 11.793)

First I tried an ANOVA, and checked for normality since I figure it won't be very normal.

```{r}
outliers_q3_un_p1 <- end_cumul_q3_un_p1 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_gross_phase)
# View(outliers_q3_un_p1) ## no outliers

aov_strategy_p1 <- aov(cumul_c_gross_phase ~ ghop_fate*pred_prod, end_cumul_q3_un_p1)

summary(aov_strategy_p1)
ggqqplot(residuals(aov_strategy_p1))

rstatix::shapiro_test(residuals(aov_strategy_p1))
```

Shapiro wilks p = 0.024 because of some high numbers on the right side. 


###### Posthoc: Tukey's

```{r}
rstatix::tukey_hsd(aov_strategy_p1) %>% 
  knitr::kable()
```

spider remains and spider excreta were significantly different (p adj = 0.004)

mantid excreta and spider excreta were significantly different (p adj = 0.039)


##### Stats: ART ANOVA (pred prod p = 0.005, F = 8.842)

I'm going to give ART ANOVA a try here also, since the data seem relatively normal.

Aligned Rank Transformation ANOVA: a non-parametric two-way factor test. 

```{r echo=TRUE}
art_strategy_p1 <- art(cumul_c_gross_phase ~ ghop_fate * pred_prod, end_cumul_q3_un_p1)

anova(art_strategy_p1)
```

Here, the effect of predator products is not significant, but the interaction is very significant.

###### Posthoc: estimate = 7.92 for remains - excreta comparison)

```{r}
art.con(art_strategy_p1, "ghop_fate:pred_prod", interaction = T, adjust = "bonferroni") %>%
  summary() %>%
  mutate(sig. = symnum(p.value, corr = FALSE, na = FALSE,
                       cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                       symbols = c("***", "**", "*", ".", " ")))
```


So this interaction significance is mainly driven by difference between mantid remains and spider excreta.

---Discussion

We see from the correlation between the mass of animal products added to the microcosm and the total C mineralized in phase 1 that 


### C) Phase 2

Here we want to compare how the decomposition of 500mg of plant litter is affected by the phase 1 deposition of animal necromass.

#### Phase 2 dynamic plots, plant necromass decomposition

This is comparing the overall effect of predators in phase 2. 

Treatments: G, MA, WA

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 2
data_strat_unscaled_p2 <- cumul_data %>%
  group_by(trt, rep) %>%
  filter(phase == 2,
         group_compute == 2) %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily)) %>%
  ungroup() 

dyn_cumul_q3_un_p2 <- data_strat_unscaled_p2 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = ghop_fate)) +
  # geom_point(aes(shape = pred_prod)) + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, phase 2 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q3_un_p2)
```

#### End of phase 2 

The analyses we'll do will be on the statistics at the end of each phase and over the entire experiment. Here are the data for phase 2.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q3_un_p2 <- data_strat_unscaled_p2 %>% 
  filter(exp_count == max(exp_count))

end_cumul_q3_un_p2 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_c_gross_phase),
            se_cumul_c_p = se(cumul_c_gross_phase),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = ghop_fate,
             label = pred_prod)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q3_un_p2, aes(x = trt, y= cumul_c_gross_phase, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('carcass', 'mantid, all', 'spider, all', 'control')) + 
  labs(title = 'C mineralized cumulatively by treatment, phase 2 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn
```

#### Trt added mass vs C mineralized

```{r}
## see if the trt added mass drove this effect
end_cumul_q3_un_p2 %>% 
  ggplot(aes(x = trt_added_mass, # *1000,
             y = cumul_c_gross_phase,
             group = trt)) + 
  geom_point(aes(color = trt)) +
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by microcosm added mass, phase 2 only',
       x = 'Original product mass (mg)',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

regress_trt_add_p2 <- lm(cumul_c_gross_phase ~ trt_added_mass * trt, # pred_prod,
                         end_cumul_q3_un_p2)
                      # filter(end_cumul_q3_un_p2, tube_id != 'WW.04'))
summary(regress_trt_add_p2)

```

If you remove the treatment var, there is still a significant effect of the amount of necromass added to each treatment. And if you remove the one outlier, the significance drops from 0.055 to 0.028 and neither had interaction effect significance.


##### ***Stats: ANOVA (shapiro p = 0.798) (ANOVA p < 0.01, F = 5.539 )

First try an ANOVA, and check for normality.

```{r}
outliers_q3_un_p2 <- end_cumul_q3_un_p2 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_c_gross_phase)
# View(outliers_q3_un_p2) ## WW.04 is a non-extreme outlier

aov_strategy_p2 <- aov(cumul_c_gross_phase ~ ghop_fate * pred_prod, end_cumul_q3_un_p2)

summary(aov_strategy_p2)
ggqqplot(residuals(aov_strategy_p2))

rstatix::shapiro_test(residuals(aov_strategy_p2))
```

Shapiro wilks p = 0.798

So actually, the data from phase 2 are more normal than phase 1, and if we use a standard ANOVA we see that treatment *does* have an effect. Which treatments?


##### ***Post-hoc: Tukey HSD

```{r}
rstatix::tukey_hsd(aov_overall_p2) %>% 
  # arrange(group2) %>% 
  knitr::kable()
```

Results:
Control tubes were different from all other treatments (and much higher). Prey carcasses didnt differ from mantid all or spider all, and vice versa. 


### --SCALED--

From the obvious effect of mass, it's worth scaling the response to the mass added (at least in phase 1)

### A) All phases

#### *) All phases dynamic plot, --WITH ERRORBARS--

```{r}
data_strat_scaled_all <- cumul_data %>%
  group_by(trt, rep) %>% ## this is a more flexible way to group by tube
  filter(group_compute == 2) %>% # for all the predator product treatments
         # trt != 'MR') %>% 
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily),
         cumul_gross_phase_scaled = cumul_c_gross_phase / trt_added_mass) %>%
  ungroup() 

data_strat_scaled_all_summ <- data_strat_scaled_all %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_gross_phase_scaled),
            se_cumul_c_p = se(cumul_gross_phase_scaled),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod),
            phase_count = first(phase_count))

dyn_cumul_q3_sc_all <- data_strat_scaled_all_summ %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = ghop_fate)) +
  geom_errorbar(data = filter(data_strat_scaled_all_summ, !(is.na(phase_count))),
                aes(ymin = mean_cumul_c_p - se_cumul_c_p,
                    ymax = mean_cumul_c_p + se_cumul_c_p, 
                    color = trt)) + 
  # geom_point(aes(shape = pred_prod)) +
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, scaled, all phases',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q3_sc_all)
```

Spider wast well above the other two treatments that were included (spider remains, and then mantid wastes, in that order)

#### End of all phases 

Here are the predator product values at the end of the experiment:

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q3_sc_all <- data_strat_scaled_all %>% 
  filter(exp_count == max(exp_count))

end_cumul_q3_sc_all %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_gross_phase_scaled),
            se_cumul_c_p = se(cumul_gross_phase_scaled),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = trt,
             label = pred_prod),
         group = interaction(ghop_fate, pred_prod)) + 
  geom_col(position = 'dodge', color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q3_sc_all, 
              aes(x = trt, y= cumul_gross_phase_scaled, group = ghop_fate),
              width = 0.2) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('mantid remains', 'mantid waste', 'spider remains', 'spider waste')) +
  labs(title = 'C mineralized cumulatively by treatment, scaled, all phases',
       x = '\nTreatment',
       y = 'C mineralization (mg)\n',
       color = 'Treatment') +
  theme_dyn

```

##### Stats: ANOVA (shapiro p << 0.001) 

First try an ANOVA, and check for normality.

```{r}
outliers_q3_sc_all <- end_cumul_q3_sc_all %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_gross_phase_scaled)
# View(outliers_q3_sc_all)
## the four mantid treatments are all extreme outliers

aov_strat_scaled_all <- aov(cumul_gross_phase_scaled ~ ghop_fate * pred_prod, end_cumul_q3_sc_all)

summary(aov_strat_scaled_all)

ggqqplot(residuals(aov_strat_scaled_all))
rstatix::shapiro_test(residuals(aov_strat_scaled_all))
```

Very not normal. Trying ART ANOVA.


##### ___Stats: ART ANOVA (ghop_fate p = 0.049, pred_prod p = 0.073, ghop_fate:pred_prod p = 0.0002)

Aligned Rank Transformation ANOVA: a non-parametric two-way factor test. 

```{r echo=TRUE}
art_strat_sc_all <- art(cumul_gross_phase_scaled ~ ghop_fate * pred_prod, end_cumul_q3_sc_all)

anova(art_strat_sc_all)
```


###### Posthoc: estimate = 27.2 for remains - excreta comparison)

```{r}
art.con(art_strat_sc_all, "ghop_fate:pred_prod", interaction = T, adjust = "bonferroni") %>%
  summary() %>%
  mutate(sig. = symnum(p.value, corr = FALSE, na = FALSE,
                       cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                       symbols = c("***", "**", "*", ".", " ")))
```

Not all contrasts present... possibly due estimates being too low?

Without MR: 
Singularity issues, so there aren't any estimates. 


### B) Phase 1... scaled

#### Phase 1 dynamic plots

This is a plot of the CO2 respiration of each relevant treatment during phase 1.

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 1
data_strat_scaled_p1 <- cumul_data %>%
  group_by(trt, rep) %>%
  filter(phase == 1,
         group_compute == 2) %>% 
         # trt != 'MR') %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily),
         cumul_gross_phase_scaled = cumul_c_gross_phase / trt_added_mass) %>%
  ungroup()
  
dyn_cumul_q3_sc_p1 <- data_strat_scaled_p1 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_gross_phase_scaled),
            se_cumul_c_p = se(cumul_gross_phase_scaled),
            ghop_fate = first(ghop_fate),
            phase_count = first(phase_count)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt)) +
  # geom_errorbar(aes(ymin = mean_cumul_c_p - se_cumul_c_p,
                 # ymax = mean_cumul_c_p + se_cumul_c_p)) + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, scaled, phase 1 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q3_sc_p1)
```


#### End of phase 1 

The analyses we'll do will be on the statistics at the end of each phase and over the entire experiment. Here are the data for phase 1.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q3_sc_p1 <- data_strat_scaled_p1 %>% 
  filter(exp_count == max(exp_count))

end_cumul_q3_sc_p1 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_gross_phase_scaled),
            se_cumul_c_p = se(cumul_gross_phase_scaled),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = trt)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q3_sc_p1, 
              aes(x = trt, y= cumul_gross_phase_scaled, group = ghop_fate),
              width = 0.2) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('mantid remains', 'mantid waste', 'spider remains', 'spider waste')) +
  labs(title = 'C mineralized cumulatively by treatment, phase 1 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn
```


##### Stats: ANOVA 
###### with MR: (shapiro << 0.001) (ghop_fate:pred_prod p = 0.001 F = 13.272)

First I tried an ANOVA, and checked for normality since I figure it won't be very normal.

```{r}
outliers_q3_sc_p1 <- end_cumul_q3_sc_p1 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_gross_phase_scaled)
# View(outliers_q3_sc_p1) ## no outliers

## dataset with outlier removed
# end_cumul_q3_sc_p1_out <- anti_join(end_cumul_q3_sc_p1, select(outliers_q3_sc_p1, tube_id))
                                   
aov_strat_scaled_p1 <- aov(cumul_gross_phase_scaled ~ ghop_fate*pred_prod,
                           end_cumul_q3_sc_p1) # end_cumul_q3_sc_p1_out)

summary(aov_strat_scaled_p1)
ggqqplot(residuals(aov_strat_scaled_p1))

rstatix::shapiro_test(residuals(aov_strat_scaled_p1))
```

__**With mantid remains treatment:**__
Shapiro wilks << 0.001, got some extreme heteroscedasticity.

Under the current model, mantid remains has the largest effect by mass, with spider wastes as #2, then spider remains and finally mantid wastes.  

If we remove the outliers (using the dataset without the four extreme outliers), ghop_fate becomes very significant (p = 0.015), and pred_prod is slightly more significant, while the interaction is still very significant. The ranking then becomes:
spider waste, 
mantid remains, 
mantid waste, 
and spider remains. 

This makes more sense. 

###### Without MR: ghop fate p = 0.001, pred_prod p << 0.001

shapiro wilks = 0.0003

ghop_fate p= 0.001
pred_prod p << 0.001

no interaction term because it's not a 2x2 


##### ***Stats: ART ANOVA 
###### With MR: (pred prod p = 0.084, F = 3.1254, ghop_fate:pred_prod p=0.0001, F= 18.0046)

Aligned Rank Transformation ANOVA: a non-parametric two-way factor test. 

```{r echo=TRUE}
art_strat_scaled_p1 <- art(cumul_gross_phase_scaled ~ ghop_fate * pred_prod, end_cumul_q3_sc_p1)

anova(art_strat_scaled_p1)
```

__**With mantid remains treatment:**__

Looking at the ART model, it gives the warning:
"F values of ANOVAs on aligned responses not of interest are not all ~0. ART may not be appropriate."

Hmmm.

Regarding the results they give, the effect of predator product type is weakly significant, while the interaction effect is very significant. 

With the extreme outliers removed, we see the same effect in the ART ANOVA, where the ghop fate becomes very significant and pred_prod remains non-significant.


###### Posthoc:
###### with MR: estimate = 7.92 for remains - excreta comparison)

```{r}
## alternatives to try the contrasts
# art.con(art_strat_scaled_p1, "ghop_fate:pred_prod")
# 
# contrast(emmeans(artlm.con(art_strat_scaled_p1, "ghop_fate:pred_prod"), ~ ghop_fatepred_prod), method = "pairwise")


art.con(art_strat_scaled_p1, "ghop_fate:pred_prod", interaction = T, adjust = "bonferroni") %>%
  summary() %>%
  mutate(sig. = symnum(p.value, corr = FALSE, na = FALSE,
                       cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                       symbols = c("***", "**", "*", ".", " ")))
```

__**With mantid remains treatment:**__

So this interaction significance is mainly driven by difference between mantid remains and spider excreta? (still missing for the contrasts on the other interaction terms)


**PROCEED TO DATA INTERPRETATION WITH CAUTION**

---Results
For the scaled mineralization values in phase 1, mantid remains had the highest means (and large variability, due to four extreme outliers that had very small amounts of treatment mass left behind). 

Predator products were weakly significant (likely due to these outliers, since the order of the treatments with the highest scaled response was mantid remains, spider excreta, widow remains, and then mantid excreta)

---Discussion

Mantid remains really skew the data here from the four outliers. If we remove the remains treatment, we see that spider wastes have the greatest effect on function per gram of waste products. 


### C) Phase 2... scaled

Here we want to compare how the decomposition of 500mg of plant litter is affected by the phase 1 deposition of animal necromass.

#### Phase 2 dynamic plots, plant necromass decomposition

This is comparing the overall effect of predators in phase 2. 

Treatments: G, MA, WA

```{r}
## the dynamic, summarized plot of cumulative C
## PHASE 2
data_strat_scaled_p2 <- cumul_data %>%
  group_by(trt, rep) %>%
  filter(phase == 2,
         group_compute == 2) %>% 
         # trt != 'MR') %>%
  mutate(cumul_c_gross_phase = cumsum(infer_tube_total_daily),
         cumul_gross_phase_scaled = cumul_c_gross_phase / trt_added_mass) %>%
  ungroup() 

dyn_cumul_q3_sc_p2 <- data_strat_scaled_p2 %>% 
  group_by(trt, exp_count) %>% 
  summarize(mean_cumul_c_p = mean(cumul_gross_phase_scaled),
            se_cumul_c_p = se(cumul_gross_phase_scaled),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = exp_count, 
             y = mean_cumul_c_p, 
             group = trt)) +
  geom_line(aes(color = trt,
                linetype = ghop_fate)) +
  # geom_point(aes(shape = pred_prod)) + 
  scale_color_viridis(name = 'Treatment', discrete = TRUE) +
  labs(title = 'C mineralized cumulatively by each tube, phase 2 only',
       x = 'Incubation Day',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn

ggplotly(dyn_cumul_q3_sc_p2)
```

#### End of phase 2 

Here are the scaled data for phase 2.

```{r}
## Data analysis: bar, end of phase plots by treatment
## same as above, in bar plot summarized form at the end of the experiment
end_cumul_q3_sc_p2 <- data_strat_scaled_p2 %>% 
  filter(exp_count == max(exp_count))

end_cumul_q3_sc_p2 %>% 
  group_by(trt) %>% 
  summarize(mean_cumul_c_p = mean(cumul_gross_phase_scaled),
            se_cumul_c_p = se(cumul_gross_phase_scaled),
            ghop_fate = first(ghop_fate),
            pred_prod = first(pred_prod)) %>% 
  ggplot(aes(x = trt, 
             y = mean_cumul_c_p, 
             fill = trt,
             label = pred_prod)) +
  geom_col(position = 'dodge',
           color = 'black')+
  geom_errorbar(aes( ymin = mean_cumul_c_p - se_cumul_c_p, 
                     ymax = mean_cumul_c_p + se_cumul_c_p,
                     width = 0.15)) +
  geom_jitter(data = end_cumul_q3_sc_p2, aes(x = trt, y= cumul_gross_phase_scaled, group = ghop_fate)) +
  scale_fill_viridis(name = 'Treatment', discrete = TRUE) +
  # scale_x_discrete(labels= bar_x_labels) +
  scale_x_discrete(labels = c('mantid, remains', 'mantid, waste', 'spider, waste', 'spider, waste')) +
  labs(title = 'C mineralized cumulatively by treatment, phase 2 only',
       x = 'Treatment',
       y = 'C mineralization (mg)',
       color = 'Treatment') +
  theme_dyn
```


##### ___Stats: ANOVA 
##### with MR: (shapiro p <<< 0.001) (interaction effect p = 0.002, F = 11.170)

First try an ANOVA, and check for normality.

```{r}
outliers_q3_sc_p2 <- end_cumul_q3_sc_p2 %>% 
  # group_by(trt) %>%
  rstatix::identify_outliers(cumul_gross_phase_scaled)
# View(outliers_q3_sc_p2) ## WW.04 is a non-extreme outlier

aov_strat_scaled_p2 <- aov(cumul_gross_phase_scaled ~ ghop_fate * pred_prod, end_cumul_q3_sc_p2)

summary(aov_strat_scaled_p2)
ggqqplot(residuals(aov_strat_scaled_p2))

rstatix::shapiro_test(residuals(aov_strat_scaled_p2))
```

Shapiro wilks p <<< 0.001

When unscaled, date from phase 2 are quite normal. When scaled to biomass however, it gets crazy unnormal. This may be due to the lower limit of the data (biomass can't be below zero), and 


##### Post-hoc: Tukey HSD for the estimate

```{r}
rstatix::tukey_hsd(aov_strat_scaled_p2) %>%     # arrange(group2) %>% 
  knitr::kable()
```

Two interactino contrasts were significant: 
mantid remains and spider remains were sig. different (p.adj = 0.006, estimate = -3987541)
mantid remains and mantid excreta were sig. different (p.adj = 0.005, estimate = -4017543)

Probably won't use this.

##### ___Stats: ART ANOVA (ghop_fate p = 0.049, pred_prod p=0.073, interaction p= 0.0002)

Aligned Rank Transformation ANOVA: a non-parametric two-way factor test. 

```{r echo=TRUE}
art_strat_scaled_p2 <- art(cumul_gross_phase_scaled ~ ghop_fate * pred_prod, end_cumul_q3_sc_p2)

anova(art_strat_scaled_p2)
```




###### Posthoc: estimate = 7.92 for remains - excreta comparison)

```{r}
art.con(art_strat_scaled_p2, "ghop_fate:pred_prod", interaction = T, adjust = "bonferroni") %>%
  summary() %>%
  mutate(sig. = symnum(p.value, corr = FALSE, na = FALSE,
                       cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                       symbols = c("***", "**", "*", ".", " ")))
```




---Results:
In phase 2, during the decomposition of plant matter, when the response was scaled to the treatment added mass, the data were very non-normal and only the interaction effect was significant (although I didn't manage to get the stats for the contrasts)


